Uncertainty Quantification and Inference of Manning's Friction Coefficient using DART Buoys Data during \tohoku Tsunami

### 2014-01-29 paper/conc.tex
Add some more conclusions and revisions
Rewrite discussion/conclusions section
Include discussion about uncertainties from source and bathymetry and
more discussion about the resultant marginal PDFs and MAP values.

%!TEX root = paper.tex
\section{Discussion and conclusions}
\label{sec:conc}

@@

In our test case, the \tohoku tsunami, we used four DART buoy gauges that provide 
surface elevation information.  To accelerate the Bayesian inference, we relied on the polynomial 
chaos expansions to produce a faithful and efficient surrogate of the forward model \geoclaw.  This PC surrogate model was then used to quantify the uncertainties in the predicted water surface elevations due to the uncertainties in the Manning's $n$ coefficient.  This included the mean an standard deviation of water surface elevations which were also compared to the measured buoy data.  A global sensitivity analysis was also performed in order to quantify the contribution of each uncertain parameter to the variance in surface elevation.  It was found that the Manning's $n$ coefficient in the near-shore region $n_2$ contributed the most to the variance in the surface elevations compared to the other two Manning's $n$ coefficients in the on-shore and deep-water regions.  Finally, using Bayesian inference, MAP estimates were found for the three region's $n$ parameters using MCMC.  These values (excluding $n_1$ where no meaningful MAP value was found), $n_2=0.011$ and $n_3=0.180$, are \comment{unexpected and different from the expected values used commonly in tsunami modeling.  This may be due to a number of other sources of uncertainty not taken into account in this analysis.}

% The main results of this work were:
% \begin{itemize}

% \item We built a surrogate model using PC expansions that required 125 forward model runs of \geoclaw.
% The surrogate model was tested, validated and proved to be faithful.

% \item We used the PC surrogate to quantify the uncertainties in the predicted water surface elevation 
% due to the uncertainties in the Manning's $n$ coefficient. To this end, we estimated the mean and the standard deviation of water surface elevation and compared it with the measured data collected at found gauges.

% \item A global sensitivity analysis was performed to quantity the contribution of each uncertain parameter to the variance in water surface elevation.  We found that the Manning’s $n$ coefficient at the shore $n_2$ is dominant and
% contributes the most to the variance in the water surface elevation compared
% to the other two Manning’s $n$ coefficients $n_1$ and $n_3$ for almost the
% entire tsunami event.

% \item We used Bayesian inference and identified the following MAP
% estimates for the three $n$ parameters using MCMC, namely $n_2=0.011$ and
% $n_3=0.180$, while for $n_1$ no meaningful MAP value could be determined from the
% available data.

% \end{itemize}

Finally, we note that the present study focused on formulating and estimating a low-dimensional representation
of the Manning's $n$ coefficient using UQ techniques namely Bayesian inference and PC expansions.  A high-dimensional representation of the Manning's $n$ coefficient would require a large number of forward runs that is computationally expensive.  Alternative methods can be implemented to reduce the dimensionality of the problem and will be the objective of a future study.

>>>>

%!TEX root = paper.tex
\section{Discussion and Conclusions}
\label{sec:conc}

@@

In our test case, the \tohoku tsunami, we used four DART buoy gauges that
provide  surface elevation information.  To accelerate the Bayesian inference,
we relied on the polynomial  chaos expansions to produce a faithful and
efficient surrogate of the forward model \geoclaw.  This PC surrogate model was
then used to quantify the uncertainties in the predicted water surface
elevations due to the uncertainties in the Manning's $n$ coefficient.  This
included the mean an standard deviation of water surface elevations which were
also compared to the measured buoy data.  A global sensitivity analysis was also
performed in order to quantify the contribution of each uncertain parameter to
the variance in surface elevation.  It was found that the Manning's $n$
coefficient in the near-shore region $n_2$ contributed the most to the variance
in the surface elevations compared to the other two Manning's $n$ coefficients
in the on-shore and deep-water regions.  This is expected as the deep-water
friction has little effect on the overall column.  On the other hand, the
sensitivity of the analysis to the on-shore value being less than that in the
deep-water was unexpected and we suspect is due primarily to the use of the
DART buoy gauges used as they are far enough away from land regions that they
would not have had as large of an impact as say if data from inundation zones
was used.

Using Bayesian inference, MAP estimates were found for the three region's $n$
parameters using MCMC.  These values were (excluding $n_1$ where no meaningful
MAP value was found), $n_2=0.011$ and $n_3=0.180$.  The values and their
corresponding marginalized PDFs (Figure~\ref{fig:pdfs}) tell perhaps the most
complete story in this analysis.  As was mentioned above, $n_2$ is the most
sensitive and has the most clear MAP value.  Although the value was lower than
expected, the tail includes the most commonly used values (0.022-0.025).  The
deep-water value $n_3$ has a peak that is much higher than expected but a tail
that does not taper off particularly quickly.  This is not altogether unexpected
due to the low sensitivity of the simulations to this region's friction.  The
on-shore value $n_1$ shows again how insensitive the simulations and
observations used were to on-shore values.

Finally, it should be noted that the friction source term is only one of a
number of other sources of uncertainty.  In particular, the rupture model and
bathymetry used can often have a larger influence on the tsunami than friction
does.  In the future, this type of analysis would be more illustrative if
propagation of uncertainties in both the bathymetry and source models were
included in each Manning's $n$ estimate.  We would also like to note that the
present study focused on formulating and estimating a low-dimensional
representation of the Manning's $n$ coefficient using UQ techniques namely
Bayesian inference and PC expansions.  A high-dimensional representation of the
Manning's $n$ coefficient would require a large number of forward runs that is
computationally expensive.  Alternative methods can be implemented to reduce the
dimensionality of the problem and will be the objective of a future study.
